paper

### 2022-03-31 outputs/paper.Rmd
update

# make dataset into long format
# rename 
caretaker <- residence %>% 
  select(-c(character, no_child_under_six, one_more_child_under_six, total, number_of_employed_women)) %>% 
  pivot_longer(!background, names_to = "caretakers", values_to = "percentage") %>% 
  mutate(caretakers = recode(caretakers,
                             'caretaker_respondent' = 'respondent',
                             'caretaker_partner' = 'partner',
                             'caretaker_other_relative' = 'other relative',
                             'caretaker_other_male_child' = 'other male child',
                             'caretaker_other_female_child' = 'other female child',
                             'caretaker_other' = 'other',
                             'caretaker_not_worked since_birth' = 'not worked since birth',
                             'caretaker_neighbor' = 'neighbour',
                             'caretaker_missing' = 'missing',
                             'caretaker_hired' = 'hired',
                             'caretaker_child_in_school' = 'child in school'))

@@

>>>>

# make dataset into long format
# rename 
caretaker <- residence %>% 
  select(-c(character, no_child_under_six, one_more_child_under_six, total, number_of_employed_women)) %>% 
  pivot_longer(!background, names_to = "caretakers", values_to = "percentage") %>% 
  mutate(caretakers = recode(caretakers,
                             'caretaker_respondent' = 'respondent',
                             'caretaker_partner' = 'partner',
                             'caretaker_other_relative' = 'other relative',
                             'caretaker_other_male_child' = 'other male child',
                             'caretaker_other_female_child' = 'other female child',
                             'caretaker_other' = 'other',
                             'caretaker_not_worked_since_birth' = 'not worked since birth',
                             'caretaker_neighbor' = 'neighbour',
                             'caretaker_missing' = 'missing',
                             'caretaker_hired' = 'hired',
                             'caretaker_child_in_school' = 'child in school'))

@@

```{r}
# region

child <- region %>% 
  select(-c(character, total)) %>% 
  pivot_longer(!background, names_to = "x", values_to = "percentage")
